Supplemental Information for\\``Heavy rainfall in Paraguay during the 2015-2016 austral summer: causes and subseasonal-to-seasonal predictive skill''

### 2018-05-06 reports/writeup/Supplement.tex
make supplemental figs fit on page

\begin{sidewaysfigure}
	\includegraphics[width=\textwidth, height=\textheight, keepaspectratio=true]{nino_sst_anomalies.pdf}
	\caption{
		Monthly SST anomalies during December of three major El Ni\~{n}o events.
		Months shown are NDJF of (a,d,g,j): 1982-83, (b,e,h,k): 1997-98, and (c,f,i,l): 2015-16.
		Units are in \si{\celsius}.
		SST data from \citet{Reynolds2002}.
		Also shown are rainfall anomalies over South America, from \citet{Xie2010}.
		Rainfall contour intervals are \SI{1}{\milli\meter\per\day}.
	}
\end{sidewaysfigure}

\begin{figure}
	\noindent\includegraphics[width=6.4in]{sst_anomalies.pdf}
	\caption{
		Pearson correlation, at monthly time step, of  sea surface temperature (SST) anomalies \citep{Reynolds2002} with four leading EOFs of \SI{850}{\hecto\pascal} streamfunction over the weather typing region, shown with a black box.
		Central Southern Atlantic Dipole is shown with a blue box.
		(a): EOF 1; (b): EOF2; (c): EOF3; (d): EOF4.
	}\label{fig:sst-anomalies}
\end{figure}

>>>>

\begin{figure}
	\noindent\includegraphics[width=6in]{sst_anomalies.pdf}
	\caption{
		Pearson correlation, at monthly time step, of  sea surface temperature (SST) anomalies \citep{Reynolds2002} with four leading EOFs of \SI{850}{\hecto\pascal} streamfunction over the weather typing region, shown with a black box.
		Central Southern Atlantic Dipole is shown with a blue box.
		(a): EOF 1; (b): EOF2; (c): EOF3; (d): EOF4.
	}\label{fig:sst-anomalies}
\end{figure}

\begin{figure}
	\includegraphics[width=\textwidth]{predictors_eofs.pdf}
	\caption{
		Spearman (rank) correlation coefficient between several S2S climate indices and weather type occurrence at monthly time step.
		These correlations are computed between the proportion of occurrence of each weather type and the monthly-mean time series of the climate index.
		For the MJO phases the monthly-mean time series is the proportion of occurrence of that phase for the given month.
		The NINO 3.4 time series was up-sampled from monthly to daily values by persisting the most recent monthly value (no interpolation).
		The SCAD predictor, labeled Dipole, is the mean meridional gradient of SST anomalies over the region \SIrange{30}{10}{\degree W} and \SIrange{40}{15}{\degree S}, up-sampled to daily values using the same method as the NINO 3.4 time series.
	}\label{fig:predictor-eof}
\end{figure}
